Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-08 paper.tex

The chord diagrams shown in \cref{fig:mornings} depict the aggregated number of queries made between any two stations on weekdays (See \cref{fig:weekdays_morning}) and weekends (See \cref{fig:weekends_morning}) respectively. 
Visualizing our dataset in this manner reveals the complexity of flows on the Belgian rail system and the significance of cities in daily travel.
%We can observe that Brussels, Antwerp, Gent and Leuven are the dominant destinations.
%Turning our attention to weekday travel, we can observe that Antwerp, Brussels and Gent are the dominant destinations.
%The reverse occurs in the evening when trips are made towards provincial stations.
Brussels City stands out as the most distinctive visual element in both figures, indicating its function as the principal centre of rail activity (see \cref{fig:mornings}a).
On a regional level, its function as a centre appears to be more distinctive for the Walloon region than Flanders.
With exception to Liège city (see \cref{fig:mornings}e), queries from the Walloon region are generally made from provincial stations towards Brussels instead of major cities within their administrative boundaries. 
Queries from Flanders, on the hand, tend to be distributed among four major cities otherwise known as the Flemish Diamond, a network of metropolitan areas in Belgium comprised of Brussels, Antwerp (see \cref{fig:mornings}b), Gent (see \cref{fig:mornings}c) and Leuven (see \cref{fig:mornings}d). 
These insights indicate that the structure of flows in Flanders appear to follow a polycentric pattern while that of the Walloon region is relatively monocentric, with Brussels as a major centre.
The difference between both regions appear to correspond with existing measures of population density and degree of urbanisation, providing valuable insight as well as alternative perspectives into the function of cities in rural and urban settings.

\begin{figure*}
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekdays_morning.pdf}\\
    \subcaption{Weekdays} % 4 words max
    \label{fig:weekdays_morning}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekends_morning.pdf}\\
    \subcaption{Weekends} % 4words max
    \label{fig:weekends_morning}
  \end{subfigure}
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \label{fig:mornings}
  \caption{\todo{Needs a caption!}}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{ccc}
  \includegraphics[width=.33\textwidth]{wd-brussels.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-antwerp.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-gent.pdf}\\
  (a) Brussels City&(b) Antwerp City&(c) Gent\\[6pt]
  \includegraphics[width=.33\textwidth]{wd-leuven.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-liege.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-mons.pdf}\\ 
  (d) Leuven&(e) Liege City&(f) Mons\\
\end{tabular}
\label{fig:cities}
\centering
\caption{\todo{Needs a caption!}}
\end{figure*}

>>>>

The chord diagrams shown in \cref{fig:mornings} depict the aggregated number of queries made between any two stations on weekdays (See \cref{fig:weekdays_morning}) and weekends (See \cref{fig:weekends_morning}) respectively. 
Visualizing our dataset in this manner reveals the complexity of flows on the Belgian rail system and the significance of cities in daily travel.
%We can observe that Brussels, Antwerp, Gent and Leuven are the dominant destinations.
%Turning our attention to weekday travel, we can observe that Antwerp, Brussels and Gent are the dominant destinations.
%The reverse occurs in the evening when trips are made towards provincial stations.
Brussels City stands out as the most distinctive visual element in both figures, indicating its function as the principal centre of rail activity (see \cref{fig:mornings}a).
On a regional level, its function as a centre appears to be more distinctive for the Walloon region than Flanders.
With exception to Liège city (see \cref{fig:mornings}e), queries from the Walloon region are generally made from provincial stations towards Brussels instead of major cities within their administrative boundaries. 
Queries from Flanders, on the hand, tend to be distributed among four major cities otherwise known as the Flemish Diamond, a network of metropolitan areas in Belgium comprised of Brussels, Antwerp (see \cref{fig:mornings}b), Gent (see \cref{fig:mornings}c) and Leuven (see \cref{fig:mornings}d). 
These insights indicate that the structure of flows in Flanders appear to follow a polycentric pattern while that of the Walloon region is relatively monocentric, with Brussels city as a major centre.
The difference between both regions appear to correspond with existing measures of population density and degree of urbanisation, providing valuable insight as well as alternative perspectives into the function of cities in rural and urban settings.

\begin{figure*}
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekdays_morning.pdf}\\
    \subcaption{Weekdays} % 4 words max
    \label{fig:weekdays_morning}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekends_morning.pdf}\\
    \subcaption{Weekends} % 4words max
    \label{fig:weekends_morning}
  \end{subfigure}
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \label{fig:mornings}
  \caption{Comparison of morning rush hour travel flows on weekdays and weekends.}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{ccc}
  \includegraphics[width=.33\textwidth]{wd-brussels.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-antwerp.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-gent.pdf}\\
  (a) Brussels City&(b) Antwerp City&(c) Gent\\[6pt]
  \includegraphics[width=.33\textwidth]{wd-leuven.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-liege.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-mons.pdf}\\ 
  (d) Leuven&(e) Liege City&(f) Mons\\
\end{tabular}
\label{fig:cities}
\centering
\caption{Comparison of morning rush hour travel flows on weekdays originating from or towards six major cities in Belgium.}
\end{figure*}
